
```{r results ='hide', warning=FALSE, message=FALSE}
library(tidyverse)
library(haven)
library(dplyr)
library(ggplot2)
library(rlist)
library(lavaan)
library(semTools)
library(gridExtra)
library(rms)
library(writexl)
library(openxlsx)
```

```{r}
load("model_data_3b.RData")
head(con_data)
```

### perform standardization transform
```{r}
model_variables <- c("PB_uw", "Trust_uw", "SB_uw", "EC_uw", "CNS_uw", "CIJM_uw", "SN_uw", "int_Interest", "int_Intention", "TB_uw", "inc_int", "edu_int", "age", "bill_fixed", "ac_score")
con_data <- con_data %>%  mutate(across(all_of(model_variables), ~ scale(.), .names = "scaled_{.col}"))
```


```{r}
head(con_data)
```

```{r}
## correlation of all observed measures
require(corrplot)
modeldata <- con_data %>% select(scaled_int_Interest, scaled_int_Intention,scaled_inc_int,liberal,scaled_PB_uw,scaled_SB_uw,scaled_Trust_uw,scaled_EC_uw,scaled_CNS_uw,scaled_CIJM_uw,scaled_SN_uw, scaled_bill_fixed, scaled_age,CCA_aware_bin,home_bin,have_solar_bin,pv_ads_bin,democrat,Female, White,attentive,col_edu)
modeldata<-na.omit(modeldata)

#calculate correlation
correlations <- cor(modeldata)

#plot correlation
png("Study3_Results/plots_uw/corr_plots.png", width = 1000, height = 1000)

corrplot(correlations, method = "color", outline = T, addgrid.col = "darkgray", order="hclust", addrect = 4, rect.col = "black", rect.lwd = 5,cl.pos = "b", tl.col = "indianred4", tl.cex = 1.5, cl.cex = 1.5, addCoef.col = "white", number.digits = 2, number.cex = 0.75, col = colorRampPalette(c("darkred","white","midnightblue"))(100))

dev.off()  # Close the graphics device
```



## Linear Regression

### linear regression using scaled values
```{r}
#function to return linear regression results

multiple_regression_summary <- function(model) {
  # Get coefficient estimates
  coefficients <- coef(model)
  
  # Get standard errors
  standard_errors <- sqrt(diag(vcov(model)))
  
  # Get p-values
  p_values <- summary(model)$coefficients[, "Pr(>|t|)"]
  
  # Calculate AIC
  aic <- AIC(model)
  
  # Calculate adjusted R-squared
  adj_r_squared <- summary(model)$adj.r.squared
  # Calculate Variance Inflation Factors (VIF)
  vif_values <- vif(model)
  
   n_observations <- nrow(model$model)
  
  # Create a summary data frame
  summary_data <- data.frame(
    Coefficient = coefficients,
    StdError = standard_errors,
    PValue = p_values,
    AIC = aic,
    AdjRSquared = adj_r_squared,
    VIF = c("NA", vif_values),
    N_Observations = n_observations
  )
  
  return(summary_data)
}
```

#### First include only message related variables and main effects
```{r}
# Fit a linear regression model for interest
model1a <- lm( scaled_int_Interest ~ RC + CCA+  scaled_PB_uw +  scaled_Trust_uw +  scaled_SB_uw, data = con_data)

# Call the function and get the results
results_model1a <- multiple_regression_summary(model1a)
results_model1a
```

```{r}
# Fit a linear regression model for interest
model1b <- lm(scaled_int_Intention ~ RC + CCA+  scaled_PB_uw +  scaled_Trust_uw +  scaled_SB_uw, data = con_data)

# Call the function and get the results
results_model1b<- multiple_regression_summary(model1b)
results_model1b
```


```{r}
#EXPORT to excel

wb1 <- createWorkbook()

update_excel <- function(workbook, sheet_name, df1, df2){

addWorksheet(workbook, sheet_name)
# Write dataframes to the worksheet with spacing
writeData(workbook, sheet_name, df1, startCol = 1, startRow = 1)
writeData(workbook, sheet_name, df2, startCol = ncol(df1) + 3, startRow = 1)
}
```

```{r}
update_excel(wb1, "Main Effects", results_model1a, results_model1b)
```

#### Second include interactions between messages and beleifs

```{r}
# Fit a logistic regression model for interest
model2a <- lm(scaled_int_Interest ~ RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw, data = con_data)

# Call the function and get the results
results_model2a <- multiple_regression_summary(model2a)
results_model2a
```

```{r}
# Fit a logistic regression model for interest
model2b <- lm(scaled_int_Intention ~ RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw, data = con_data)

# Call the function and get the results
results_model2b <- multiple_regression_summary(model2b)
results_model2b
```

```{r}
update_excel(wb1, "All Interactions", results_model2a, results_model2b)
```

```{r}
model3a <- lm(scaled_int_Interest ~ RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw , data = con_data)

results_model3a <- multiple_regression_summary(model3a)
results_model3a
```


```{r}
model3b <- lm(scaled_int_Intention ~ RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw , data = con_data)

results_model3b <- multiple_regression_summary(model3b)
results_model3b
```
```{r}
update_excel(wb1, "all beliefs and interactions", results_model3a, results_model3b)
```

```{r}
model4a <- lm(scaled_int_Interest ~ RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw + scaled_inc_int + scaled_edu_int + scaled_age, data = con_data)

results_model4a <- multiple_regression_summary(model4a)
results_model4a
```

```{r}
model4b <- lm(scaled_int_Intention  ~ RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw + scaled_inc_int + scaled_edu_int + scaled_age + home_bin, data = con_data)

results_model4b <- multiple_regression_summary(model4b)
results_model4b
```

```{r}
update_excel(wb1, "all variables", results_model4a, results_model4b)
```

```{r}
#export excel sheet
saveWorkbook(wb1, "Study3_Results/plots_uw/Linear_Reg_all_sample.xlsx", overwrite = TRUE)
```

## Filter out homeowners

```{r}
#repeat anovas time time filtering for homeowners
homeowners_con_data <- con_data %>% filter(home_bin == 1)
```



#### First include only message related variables and main effects
```{r}
# Fit a logistic regression model for interest
model1a <- lm( int_Interest ~ RC + CCA+  scaled_PB_uw +  scaled_Trust_uw +  scaled_SB_uw, data =  homeowners_con_data)

# Call the function and get the results
results_model1a <- multiple_regression_summary(model1a)
#results_model1a

```
```{r}
# Fit a logistic regression model for interest
model1b <- lm(scaled_int_Intention ~ RC + CCA + scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw, data =  homeowners_con_data)

# Call the function and get the results
results_model1b<- multiple_regression_summary(model1b)
#results_model1b
```
```{r}
#EXPORT to excel

wb2 <- createWorkbook()

```


```{r}
update_excel(wb2, "Main Effects", results_model1a, results_model1b)
```

#### Second include interactions between messages

```{r}
# Fit a logistic regression model for interest
model2a <- lm(scaled_int_Interest ~ RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw, data =  homeowners_con_data)

# Call the function and get the results
results_model2a <- multiple_regression_summary(model2a)
#results_model2a
```

```{r}
# Fit a logistic regression model for interest
model2b <- lm(scaled_int_Intention ~ RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw, data =  homeowners_con_data)

# Call the function and get the results
results_model2b <- multiple_regression_summary(model2b)
#results_model2b
```

```{r}
update_excel(wb2, "Message Interactions", results_model2a, results_model2b)
```

#### Third include interactions between messages and beliefs

```{r}
model3a <- lm(scaled_int_Interest ~  RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw, data =  homeowners_con_data)

results_model3a <- multiple_regression_summary(model3a)
results_model3a
```

```{r}
model3b <- lm(scaled_int_Intention  ~  RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw , data =  homeowners_con_data)

results_model3b <- multiple_regression_summary(model3b)
results_model3b
```

```{r}
update_excel(wb2, "all Interactions", results_model3a, results_model3b)
```

#### Fourth Model everything

```{r}
model4a <- lm(scaled_int_Interest ~ RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw+ scaled_inc_int + scaled_edu_int + scaled_age, data = homeowners_con_data)

results_model4a <- multiple_regression_summary(model4a)
results_model4a
```


```{r}
model4b <- lm(scaled_int_Intention  ~ RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw+ scaled_inc_int + scaled_edu_int + scaled_age, data = homeowners_con_data)

results_model4b <- multiple_regression_summary(model4b)
results_model4b
```

```{r}
update_excel(wb2, "all variables", results_model4a, results_model4b)  
```
```{r}
#export excel sheet
saveWorkbook(wb2, "Study3_Results/plots_uw/Linear_Reg_homeowners.xlsx", overwrite = TRUE)
```


## Modeling by controlling for PV ownership

```{r}
#repeat anovas time time filtering for homeowners
pvowners_con_data <- con_data %>% filter(have_solar_bin == 0)
```
##  ANOVA

### One-way ANOVA

```{r}
# Perform two-way ANOVA
anova_interest <- aov(scaled_int_Interest ~ RC + CCA, data = pvowners_con_data)


anova_intention <- aov(scaled_int_Intention ~  CCA, data = pvowners_con_data)
# Display ANOVA summary
#summary(anova_interest)
summary(anova_intention)
```

#### First include only message related variables and main effects
```{r}
# Fit a logistic regression model for interest
model1a <- lm( int_Interest ~ RC + CCA+  scaled_PB_uw +  scaled_Trust_uw +  scaled_SB_uw, data =  pvowners_con_data)

# Call the function and get the results
results_model1a <- multiple_regression_summary(model1a)
summary(model1a)

```
```{r}
# Fit a logistic regression model for interest
model1b <- lm(scaled_int_Intention ~ RC + CCA+  scaled_PB_uw +  scaled_Trust_uw +  scaled_SB_uw, data =  pvowners_con_data)

# Call the function and get the results
results_model1b<- multiple_regression_summary(model1b)
summary(model1b)
```


```{r}
#EXPORT to excel

wb3 <- createWorkbook()

```


```{r}
update_excel(wb3, "Main Effects", results_model1a, results_model1b)
```

#### Second include interactions between messages

```{r}
# Fit a logistic regression model for interest
model2a <- lm(scaled_int_Interest ~ RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw, data =  pvowners_con_data)

# Call the function and get the results
results_model2a <- multiple_regression_summary(model2a)
#summary(model2a)
```

```{r}
# Fit a logistic regression model for interest
model2b <- lm(scaled_int_Intention ~ RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw, data =  pvowners_con_data)

# Call the function and get the results
results_model2b <- multiple_regression_summary(model2b)
#summary(model2b)
```

```{r}
update_excel(wb3, "Message Interactions", results_model2a, results_model2b)
```

#### Third include interactions between messages and beliefs

```{r}
model3a <- lm(scaled_int_Interest ~  RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw, data =  pvowners_con_data)

results_model3a <- multiple_regression_summary(model3a)
summary(model3a)
```
```{r}
results_model3a
```

```{r}
model3b <- lm(scaled_int_Intention  ~  RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw, data =  pvowners_con_data)

results_model3b <- multiple_regression_summary(model3b)
summary(model3b)
```

```{r}
update_excel(wb3, "all Interactions", results_model3a, results_model3b)
```

```{r}
model4a <- lm(scaled_int_Interest  ~  RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw+ scaled_inc_int + scaled_edu_int + scaled_age + attentive+ home_bin, data =  pvowners_con_data)

#results_model4a <- multiple_regression_summary(model4a)
summary(model4a)
```

```{r}
model4b <- lm(scaled_int_Intention  ~  RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw+ scaled_inc_int + scaled_edu_int + scaled_age + attentive+ home_bin, data =  pvowners_con_data)

results_model4b <- multiple_regression_summary(model4b)
summary(model4b)
```

```{r}
update_excel(wb3, "all variables", results_model4a, results_model4b)  
```

```{r}
#export excel sheet
saveWorkbook(wb3, "Study3_Results/plots_uw/Linear_Reg_nopvowners.xlsx", overwrite = TRUE)
```

## Modeling by controlling for attentiveness

```{r}
#repeat anovas time time filtering for homeowners
attentive_con_data <- con_data %>% filter(attentive == 1)
```


#### First include only message related variables and main effects
```{r}
# Fit a logistic regression model for interest
model1a <- lm( int_Interest ~ RC + CCA+  scaled_PB_uw +  scaled_Trust_uw +  scaled_SB_uw, data =  attentive_con_data)

# Call the function and get the results
results_model1a <- multiple_regression_summary(model1a)
#results_model1a

```
```{r}
# Fit a logistic regression model for interest
model1b <- lm(scaled_int_Intention ~ RC + CCA+  scaled_PB_uw +  scaled_Trust_uw +  scaled_SB_uw, data =  attentive_con_data)

# Call the function and get the results
results_model1b<- multiple_regression_summary(model1b)
#results_model1b
```


```{r}
#EXPORT to excel

wb4 <- createWorkbook()

```


```{r}
update_excel(wb4, "Main Effects", results_model1a, results_model1b)
```

#### Second include interactions between messages

```{r}
# Fit a logistic regression model for interest
model2a <- lm(scaled_int_Interest ~ RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw, data =  attentive_con_data)

# Call the function and get the results
results_model2a <- multiple_regression_summary(model2a)
results_model2a
```

```{r}
# Fit a logistic regression model for interest
model2b <- lm(scaled_int_Intention ~ RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw, data =  attentive_con_data)

# Call the function and get the results
results_model2b <- multiple_regression_summary(model2b)
results_model2b
```

```{r}
update_excel(wb4, "Message Interactions", results_model2a, results_model2b)
```

#### Third include interactions between messages and beliefs

```{r}
model3a <- lm(scaled_int_Interest ~  RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw, data =  attentive_con_data)

results_model3a <- multiple_regression_summary(model3a)
results_model3a
```

```{r}
model3b <- lm(scaled_int_Intention  ~  RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw, data =  attentive_con_data)

results_model3b <- multiple_regression_summary(model3b)
#results_model3b
```

```{r}
update_excel(wb4, "all Interactions", results_model3a, results_model3b)
```

```{r}
model4a <- lm(scaled_int_Interest  ~  RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw+ scaled_inc_int + scaled_edu_int + scaled_age, data =  attentive_con_data)

results_model4a <- multiple_regression_summary(model4a)
results_model4a
```

```{r}
model4b <- lm(scaled_int_Intention  ~  RC + CCA + RC*CCA+ scaled_PB_uw + scaled_Trust_uw + scaled_SB_uw + RC*scaled_PB_uw+ RC*scaled_SB_uw + CCA*scaled_Trust_uw+ RC*scaled_Trust_uw + scaled_SN_uw + scaled_EC_uw  + scaled_CNS_uw + scaled_CIJM_uw + scaled_TB_uw+ scaled_inc_int + scaled_edu_int + scaled_age, data =  attentive_con_data)

results_model4b <- multiple_regression_summary(model4b)
#results_model4b
```

```{r}
update_excel(wb4, "all variables", results_model4a, results_model4b)  
```

```{r}
#export excel sheet
saveWorkbook(wb4, "Study3_Results/plots_uw/Linear_Reg_attentive.xlsx", overwrite = TRUE)
```

```{r}
save(pvowners_con_data, file = "final_data.RData")
```