---
title: "Sloan Study 3a Modelling"
output: html_notebook
---

```{r results ='hide', warning=FALSE, message=FALSE}
library(tidyverse)
library(haven)
library(dplyr)
library(ggplot2)
library(rlist)
library(lavaan)
library(semTools)
library(gridExtra)
library(rms)
library(writexl)
```

```{r}
load("model_data_3a.RData")
head(con_data)
```

### Create binary dependent variables

```{r}
#create binary variable for dependent values as linear regression would not be possible

con_data <- con_data %>% mutate(interest_bin = if_else(int_Interest >= 6, 1, 0, missing = NULL))

con_data <- con_data %>% mutate(intention_bin = if_else(int_Intention >= 6, 1, 0, missing = NULL))

head(con_data)
```
### peform standardization transform
```{r}
model_variables <- c("PB_w", "Trust_w", "SB_w", "EC_w", "CNS_w", "CIJM_w", "SN_w", "int_Interest", "int_Intention", "TB_w", "inc_int", "edu_int", "age", "bill", "ac_score")
con_data <- con_data %>%  mutate(across(all_of(model_variables), ~ scale(.), .names = "scaled_{.col}"))
```

```{r}
head(con_data)
```

## Models with whole sample


### Create logit models


```{r}
calculate_logit_metrics <- function(model) {
  # Get coefficient estimates and standard errors
  coefficients <- coef(model)
  standard_errors <- summary(model)$coefficients[, "Std. Error"]

  # Convert coefficients to odds ratios
  odds_ratios <- exp(coefficients)

  # Calculate confidence intervals for odds ratios
  lower_ci <- exp(coefficients - 1.96 * standard_errors)
  upper_ci <- exp(coefficients + 1.96 * standard_errors)

  # Get p-values of odds ratios
  p_values <- summary(model)$coefficients[, "Pr(>|z|)"]
  
   # Calculate log-likelihood
  log_likelihood <- logLik(model)

  # Calculate AIC
  aic <- AIC(model)

  # Calculate Pseudo R-squared (Cox-Snell or Nagelkerke)
  deviance_residual <- model$null.deviance - model$deviance 
  pseudo_r_squared <- deviance_residual / model$null.deviance

  # Create a data frame to store results
  results <- data.frame(
    OddsRatio = odds_ratios,
    PValue = p_values,
    StdError = standard_errors,
    LogLikelihood = log_likelihood,
    AIC = aic,
    PseudoRSquared = pseudo_r_squared
  )

  return(results)
}

```

#### First include only message related variables
```{r}
# Fit a logistic regression model
model_messagesvsint1 <- glm(interest_bin ~ RC + CCA+  scaled_PB_w +  scaled_Trust_w +  scaled_SB_w + scaled_EC_w+  scaled_CNS_w +  scaled_CIJM_w +  scaled_SN_w +  scaled_TB_w +  scaled_inc_int+ scaled_edu_int +  scaled_age + scaled_bill, data = con_data, family = binomial)

# Call the function and get the results
results_model_messagesvsint1 <- calculate_logit_metrics(model_messagesvsint1)
results_model_messagesvsint1
```


```{r}
# Call the function and get the results
# Fit a logistic regression model
model_messagesvsint2 <- glm(intention_bin ~ RC + CCA+  scaled_PB_w +  scaled_Trust_w +  scaled_SB_w + scaled_EC_w+  scaled_CNS_w +  scaled_CIJM_w +  scaled_SN_w +  scaled_TB_w +  scaled_inc_int+ scaled_edu_int +  scaled_age + scaled_bill, data = con_data, family = binomial)

results_model_messagesvsint2 <- calculate_logit_metrics(model_messagesvsint2)
results_model_messagesvsint2
```


#### Second include belief variables as main effects and message related variables
```{r}
model_beliefsvsint1 <- glm(interest_bin ~ RC + CCA + RC*CCA+ scaled_PB_w + scaled_Trust_w + scaled_SB_w + scaled_EC_w+ scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data = con_data, family = binomial)

results_model_beliefsvsint1<- calculate_logit_metrics(model_beliefsvsint1)
results_model_beliefsvsint1
```

```{r}
model_beliefsvsint2 <- glm(intention_bin ~ RC + CCA + RC*CCA+ scaled_PB_w + scaled_Trust_w + scaled_SB_w + scaled_EC_w+ scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data = con_data, family = binomial)

results_model_beliefsvsint2<- calculate_logit_metrics(model_beliefsvsint2)
results_model_beliefsvsint2
```
### Third, message related variables with interaction with beliefs
```{r}
model_beliefs_messagevsint1 <- glm(interest_bin ~ RC + CCA + RC*CCA + scaled_PB_w + RC*scaled_PB_w + scaled_SB_w + RC*scaled_SB_w + scaled_Trust_w + CCA*scaled_Trust_w + RC*scaled_Trust_w + scaled_EC_w  + scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data = con_data, family = binomial)

results_model_beliefs_messagevsint1 <- calculate_logit_metrics(model_beliefs_messagevsint1)
results_model_beliefs_messagevsint1 
```

```{r}
model_beliefs_messagevsint2 <- glm(intention_bin ~ RC + CCA + RC*CCA + scaled_PB_w + RC*scaled_PB_w + scaled_SB_w + RC*scaled_SB_w + scaled_Trust_w + CCA*scaled_Trust_w + RC*scaled_Trust_w + scaled_EC_w  + scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data = con_data, family = binomial)


results_model_beliefs_messagevsint2 <- calculate_logit_metrics(model_beliefs_messagevsint2)
results_model_beliefs_messagevsint2
```


### Fourth just main effects and demographic variables

```{r}
model_maineffectsvsint1 <- glm(interest_bin ~ RC + CCA_aware_bin + PB_w + SB_w + Trust_w + EC_w  + CNS_w + CIJM_w + SN_w + TB_w + col_edu + inc_int + bill_fixed + Female + White + liberal + democrat + age, data = con_data, family = binomial)

results_model_maineffectsvsint1 <- calculate_logit_metrics(model_maineffectsvsint1)
results_model_maineffectsvsint1
```

```{r}
model_maineffectsvsint2 <- glm(intention_bin ~ RC + CCA_aware_bin + PB_w + SB_w + Trust_w + EC_w  + CNS_w + CIJM_w + SN_w + TB_w + col_edu + inc_int + bill_fixed + Female + White + liberal + democrat + age, data = con_data, family = binomial)

results_model_maineffectsvsint2 <- calculate_logit_metrics(model_maineffectsvsint2)
results_model_maineffectsvsint2
```

### Anovas to measure the effect of messages
```{r}
# Perform two-way ANOVA
anova_interest <- aov(int_Interest ~ RC + CCA_fact + RC:CCA_fact, data = con_data)


anova_intention <- aov(int_Intention ~ RC + CCA_fact + RC:CCA_fact, data = con_data)
# Display ANOVA summary
summary(anova_interest)
summary(anova_intention)
```


## Modeling by controlling for homeownership
```{r}
#repeat anovas time time filtering for homeowners
homeowners_con_data <- con_data %>% filter(home_bin == 1)
```

#### First include only message related variables
```{r}
# Fit a logistic regression model
model_messagesvsint1 <- glm(interest_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin, data = homeowners_con_data, family = binomial)

# Call the function and get the results
results_model_messagesvsint1 <- calculate_logit_metrics(model_messagesvsint1)
results_model_messagesvsint1
```


```{r}
# Call the function and get the results
# Fit a logistic regression model
model_messagesvsint2 <- glm(intention_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin, data = homeowners_con_data, family = binomial)

results_model_messagesvsint2 <- calculate_logit_metrics(model_messagesvsint2)
results_model_messagesvsint2
```


#### Second include belief variables as main effects and message related variables
```{r}
model_beliefsvsint1 <- glm(interest_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin + PB_w + SB_w + Trust_w + EC_w + CNS_w + CIJM_w + SN_w + TB_w, data = homeowners_con_data, family = binomial)

results_model_beliefsvsint1<- calculate_logit_metrics(model_beliefsvsint1)
results_model_beliefsvsint1
```

```{r}
model_beliefsvsint2 <- glm(intention_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin + PB_w + SB_w + Trust_w + EC_w + CNS_w + CIJM_w + SN_w + TB_w, data = homeowners_con_data, family = binomial)

results_model_beliefsvsint2<- calculate_logit_metrics(model_beliefsvsint2)
results_model_beliefsvsint2
```
### Third, message related variables with interaction with beliefs
```{r}
model_beliefs_messagevsint1 <- glm(interest_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin + PB_w + RC*PB_w + SB_w + RC*SB_w + Trust_w + CCA_aware_bin*Trust_w + RC*Trust_w + EC_w  + CNS_w + CIJM_w + SN_w + TB_w, data = homeowners_con_data, family = binomial)

results_model_beliefs_messagevsint1 <- calculate_logit_metrics(model_beliefs_messagevsint1 )
results_model_beliefs_messagevsint1 
```

```{r}
model_beliefs_messagevsint2 <- glm(intention_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin + PB_w + RC*PB_w + SB_w + RC*SB_w + Trust_w + CCA_aware_bin*Trust_w + RC*Trust_w + EC_w  + CNS_w + CIJM_w + SN_w + TB_w, data = homeowners_con_data, family = binomial)


results_model_beliefs_messagevsint2 <- calculate_logit_metrics(model_beliefs_messagevsint2)
results_model_beliefs_messagevsint2
```


### Fourth just main effects and demographic variables

```{r}
model_maineffectsvsint1 <- glm(interest_bin ~ RC + CCA_aware_bin + PB_w + SB_w + Trust_w + EC_w  + CNS_w + CIJM_w + SN_w + TB_w + col_edu + inc_int + bill_fixed + Female + White + liberal + democrat + age, data = homeowners_con_data, family = binomial)

results_model_maineffectsvsint1 <- calculate_logit_metrics(model_maineffectsvsint1)
results_model_maineffectsvsint1
```

```{r}
model_maineffectsvsint2 <- glm(intention_bin ~ RC + CCA_aware_bin + PB_w + SB_w + Trust_w + EC_w  + CNS_w + CIJM_w + SN_w + TB_w + col_edu + inc_int + bill_fixed + Female + White + liberal + democrat + age, data = homeowners_con_data, family = binomial)

results_model_maineffectsvsint2 <- calculate_logit_metrics(model_maineffectsvsint2)
results_model_maineffectsvsint2
```

## Modeling by controlling for PV ownership

```{r}
#repeat anovas time time filtering for homeowners
pvowners_con_data <- con_data %>% filter(have_solar_bin == 0)
```

#### First include only message related variables
```{r}
# Fit a logistic regression model
model_messagesvsint1 <- glm(interest_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin, data = pvowners_con_data, family = binomial)

# Call the function and get the results
results_model_messagesvsint1 <- calculate_logit_metrics(model_messagesvsint1)
results_model_messagesvsint1
```


```{r}
# Call the function and get the results
# Fit a logistic regression model
model_messagesvsint2 <- glm(intention_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin, data = pvowners_con_data, family = binomial)

results_model_messagesvsint2 <- calculate_logit_metrics(model_messagesvsint2)
results_model_messagesvsint2
```


#### Second include belief variables as main effects and message related variables
```{r}
model_beliefsvsint1 <- glm(interest_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin + PB_w + SB_w + Trust_w + EC_w + CNS_w + CIJM_w + SN_w + TB_w, data = pvowners_con_data, family = binomial)

results_model_beliefsvsint1<- calculate_logit_metrics(model_beliefsvsint1)
results_model_beliefsvsint1
```

```{r}
model_beliefsvsint2 <- glm(intention_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin + PB_w + SB_w + Trust_w + EC_w + CNS_w + CIJM_w + SN_w + TB_w, data = pvowners_con_data, family = binomial)

results_model_beliefsvsint2<- calculate_logit_metrics(model_beliefsvsint2)
results_model_beliefsvsint2
```
### Third, message related variables with interaction with beliefs
```{r}
model_beliefs_messagevsint1 <- glm(interest_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin + PB_w + RC*PB_w + SB_w + RC*SB_w + Trust_w + CCA_aware_bin*Trust_w + RC*Trust_w + EC_w  + CNS_w + CIJM_w + SN_w + TB_w, data = pvowners_con_data, family = binomial)

results_model_beliefs_messagevsint1 <- calculate_logit_metrics(model_beliefs_messagevsint1 )
results_model_beliefs_messagevsint1 
```

```{r}
model_beliefs_messagevsint2 <- glm(intention_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin + PB_w + RC*PB_w + SB_w + RC*SB_w + Trust_w + CCA_aware_bin*Trust_w + RC*Trust_w + EC_w  + CNS_w + CIJM_w + SN_w + TB_w, data = pvowners_con_data, family = binomial)


results_model_beliefs_messagevsint2 <- calculate_logit_metrics(model_beliefs_messagevsint2)
results_model_beliefs_messagevsint2
```


### Fourth just main effects and demographic variables

```{r}
model_maineffectsvsint1 <- glm(interest_bin ~ RC + CCA_aware_bin + PB_w + SB_w + Trust_w + EC_w  + CNS_w + CIJM_w + SN_w + TB_w + col_edu + inc_int + bill_fixed + Female + White + liberal + democrat + age, data = pvowners_con_data, family = binomial)

results_model_maineffectsvsint1 <- calculate_logit_metrics(model_maineffectsvsint1)
results_model_maineffectsvsint1
```

```{r}
model_maineffectsvsint2 <- glm(intention_bin ~ RC + CCA_aware_bin + PB_w + SB_w + Trust_w + EC_w  + CNS_w + CIJM_w + SN_w + TB_w + col_edu + inc_int + bill_fixed + Female + White + liberal + democrat + age, data = pvowners_con_data, family = binomial)

results_model_maineffectsvsint2 <- calculate_logit_metrics(model_maineffectsvsint2)
results_model_maineffectsvsint2
```


## Modeling by controlling for attentiveness


```{r}
#repeat anovas time time filtering for homeowners
attentive_con_data <- con_data %>% filter(attentive == 1)
```

#### First include only message related variables
```{r}
# Fit a logistic regression model
model_messagesvsint1 <- glm(interest_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin, data = attentive_con_data, family = binomial)

# Call the function and get the results
results_model_messagesvsint1 <- calculate_logit_metrics(model_messagesvsint1)
results_model_messagesvsint1
```


```{r}
# Call the function and get the results
# Fit a logistic regression model
model_messagesvsint2 <- glm(intention_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin, data = attentive_con_data, family = binomial)

results_model_messagesvsint2 <- calculate_logit_metrics(model_messagesvsint2)
results_model_messagesvsint2
```


#### Second include belief variables as main effects and message related variables
```{r}
model_beliefsvsint1 <- glm(interest_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin + PB_w + SB_w + Trust_w + EC_w + CNS_w + CIJM_w + SN_w + TB_w, data = attentive_con_data, family = binomial)

results_model_beliefsvsint1<- calculate_logit_metrics(model_beliefsvsint1)
results_model_beliefsvsint1
```

```{r}
model_beliefsvsint2 <- glm(intention_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin + PB_w + SB_w + Trust_w + EC_w + CNS_w + CIJM_w + SN_w + TB_w, data = attentive_con_data, family = binomial)

results_model_beliefsvsint2<- calculate_logit_metrics(model_beliefsvsint2)
results_model_beliefsvsint2
```
### Third, message related variables with interaction with beliefs
```{r}
model_beliefs_messagevsint1 <- glm(interest_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin + PB_w + RC*PB_w + SB_w + RC*SB_w + Trust_w + CCA_aware_bin*Trust_w + RC*Trust_w + EC_w  + CNS_w + CIJM_w + SN_w + TB_w, data = attentive_con_data, family = binomial)

results_model_beliefs_messagevsint1 <- calculate_logit_metrics(model_beliefs_messagevsint1 )
results_model_beliefs_messagevsint1 
```

```{r}
model_beliefs_messagevsint2 <- glm(intention_bin ~ RC + CCA_aware_bin + RC*CCA_aware_bin + PB_w + RC*PB_w + SB_w + RC*SB_w + Trust_w + CCA_aware_bin*Trust_w + RC*Trust_w + EC_w  + CNS_w + CIJM_w + SN_w + TB_w, data = attentive_con_data, family = binomial)


results_model_beliefs_messagevsint2 <- calculate_logit_metrics(model_beliefs_messagevsint2)
results_model_beliefs_messagevsint2
```


### Fourth just main effects and demographic variables

```{r}
model_maineffectsvsint1 <- glm(interest_bin ~ RC + CCA_aware_bin + PB_w + SB_w + Trust_w + EC_w  + CNS_w + CIJM_w + SN_w + TB_w + col_edu + inc_int + bill_fixed + Female + White + liberal + democrat + age, data = attentive_con_data, family = binomial)

results_model_maineffectsvsint1 <- calculate_logit_metrics(model_maineffectsvsint1)
results_model_maineffectsvsint1
```

```{r}
model_maineffectsvsint2 <- glm(intention_bin ~ RC + CCA_aware_bin + PB_w + SB_w + Trust_w + EC_w  + CNS_w + CIJM_w + SN_w + TB_w + col_edu + inc_int + bill_fixed + Female + White + liberal + democrat + age, data = attentive_con_data, family = binomial)

results_model_maineffectsvsint2 <- calculate_logit_metrics(model_maineffectsvsint2)
results_model_maineffectsvsint2
```
