---
title: "Study 3 ANOVAS and MLR"
output: html_notebook
---

```{r results ='hide', warning=FALSE, message=FALSE}
library(tidyverse)
library(haven)
library(dplyr)
library(ggplot2)
library(rlist)
library(lavaan)
library(semTools)
library(gridExtra)
library(rms)
library(writexl)
library(openxlsx)
```

```{r}
load("model_data_3a.RData")
head(con_data)
```
### peform standardization transform
```{r}
model_variables <- c("PB_w", "Trust_w", "SB_w", "EC_w", "CNS_w", "CIJM_w", "SN_w", "int_Interest", "int_Intention", "TB_w", "inc_int", "edu_int", "age", "bill", "ac_score")
con_data <- con_data %>%  mutate(across(all_of(model_variables), ~ scale(.), .names = "scaled_{.col}"))
```

```{r}
head(con_data)
```

## ANOVAS


### 1. ANOVA with scaled dependent variables
```{r}
# Perform two-way ANOVA
anova_interest <- aov(scaled_int_Interest ~ RC + CCA+ RC:CCA, data = con_data)


anova_intention <- aov(scaled_int_Intention ~ RC + CCA + RC:CCA, data = con_data)
# Display ANOVA summary
summary(anova_interest)
summary(anova_intention)
```

## Linear Regression

### linear regression using scaled values
```{r}
#function to return linear regression results

multiple_regression_summary <- function(model) {
  # Get coefficient estimates
  coefficients <- coef(model)
  
  # Get standard errors
  standard_errors <- sqrt(diag(vcov(model)))
  
  # Get p-values
  p_values <- summary(model)$coefficients[, "Pr(>|t|)"]
  
  # Calculate AIC
  aic <- AIC(model)
  
  # Calculate adjusted R-squared
  adj_r_squared <- summary(model)$adj.r.squared
  # Calculate Variance Inflation Factors (VIF)
  vif_values <- vif(model)
  
   n_observations <- nrow(model$model)
  
  # Create a summary data frame
  summary_data <- data.frame(
    Coefficient = coefficients,
    StdError = standard_errors,
    PValue = p_values,
    AIC = aic,
    AdjRSquared = adj_r_squared,
    VIF = c("NA", vif_values),
    N_Observations = n_observations
  )
  
  return(summary_data)
}
```

#### First include only message related variables and main effects
```{r}
# Fit a linear regression model for interest
model1a <- lm( scaled_int_Interest ~ RC + CCA+  scaled_PB_w +  scaled_Trust_w +  scaled_SB_w, data = con_data)

# Call the function and get the results
results_model1a <- multiple_regression_summary(model1a)
results_model1a

```
```{r}
# Fit a linear regression model for interest
model1b <- lm(scaled_int_Intention ~ RC + CCA+  scaled_PB_w +  scaled_Trust_w +  scaled_SB_w, data = con_data)

# Call the function and get the results
results_model1b<- multiple_regression_summary(model1b)
results_model1b
```
```{r}
#EXPORT to excel

wb1 <- createWorkbook()

update_excel <- function(workbook, sheet_name, df1, df2){

addWorksheet(workbook, sheet_name)
# Write dataframes to the worksheet with spacing
writeData(workbook, sheet_name, df1, startCol = 1, startRow = 1)
writeData(workbook, sheet_name, df2, startCol = ncol(df1) + 3, startRow = 1)
}
```


```{r}
update_excel(wb1, "Main Effects", results_model1a, results_model1b)
```

#### Second include interactions between messages

```{r}
# Fit a logistic regression model for interest
model2a <- lm(scaled_int_Interest ~ RC + CCA + RC*CCA+ scaled_PB_w*RC + scaled_Trust_w*RC+ scaled_Trust_w*CCA + scaled_SB_w*RC, data = con_data)

# Call the function and get the results
results_model2a <- multiple_regression_summary(model2a)
results_model2a
```

```{r}
# Fit a logistic regression model for interest
model2b <- lm(scaled_int_Intention ~ RC + CCA + RC*CCA+ scaled_PB_w*RC + scaled_Trust_w*RC+ scaled_Trust_w*CCA + scaled_SB_w*RC, data = con_data)

# Call the function and get the results
results_model2b <- multiple_regression_summary(model2b)
results_model2b
```

```{r}
update_excel(wb1, "Message Interactions", results_model2a, results_model2b)
```

#### Third include interactions between messages and beliefs

```{r}
model3a <- lm(scaled_int_Interest ~ RC + CCA + RC*CCA + scaled_PB_w + RC*scaled_PB_w + scaled_SB_w + RC*scaled_SB_w + scaled_Trust_w + CCA*scaled_Trust_w + RC*scaled_Trust_w + scaled_EC_w  + scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w , data = con_data)

results_model3a <- multiple_regression_summary(model3a)
results_model3a
```

```{r}
model3b <- lm(scaled_int_Intention  ~ RC + CCA + RC*CCA + scaled_PB_w + RC*scaled_PB_w + scaled_SB_w + RC*scaled_SB_w + scaled_Trust_w + CCA*scaled_Trust_w + RC*scaled_Trust_w + scaled_EC_w  + scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w , data = con_data)

results_model3b <- multiple_regression_summary(model3b)
results_model3b
```

```{r}
update_excel(wb1, "all Interactions", results_model3a, results_model3b)
```


```{r}
#export excel sheet
saveWorkbook(wb1, "Study3_Results/Linear_Reg_all_sample.xlsx", overwrite = TRUE)
```

## Filter out homeowners

```{r}
#repeat anovas time time filtering for homeowners
homeowners_con_data <- con_data %>% filter(home_bin == 1)
```



#### First include only message related variables and maon effects
```{r}
# Fit a logistic regression model for interest
model1a <- lm( int_Interest ~ RC + CCA+  scaled_PB_w +  scaled_Trust_w +  scaled_SB_w + scaled_EC_w+  scaled_CNS_w +  scaled_CIJM_w +  scaled_SN_w +  scaled_TB_w +  scaled_inc_int+ scaled_edu_int +  scaled_age + scaled_bill, data =  homeowners_con_data)

# Call the function and get the results
results_model1a <- multiple_regression_summary(model1a)
#results_model1a

```
```{r}
# Fit a logistic regression model for interest
model1b <- lm(scaled_int_Intention ~ RC + CCA + scaled_PB_w + scaled_Trust_w + scaled_SB_w + scaled_EC_w+ scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  homeowners_con_data)

# Call the function and get the results
results_model1b<- multiple_regression_summary(model1b)
#results_model1b
```
```{r}
#EXPORT to excel

wb2 <- createWorkbook()

```


```{r}
update_excel(wb2, "Main Effects", results_model1a, results_model1b)
```

#### Second include interactions between messages

```{r}
# Fit a logistic regression model for interest
model2a <- lm(scaled_int_Interest ~ RC + CCA + RC*CCA+ scaled_PB_w + scaled_Trust_w + scaled_SB_w + scaled_EC_w+ scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  homeowners_con_data)

# Call the function and get the results
results_model2a <- multiple_regression_summary(model2a)
#results_model2a
```

```{r}
# Fit a logistic regression model for interest
model2b <- lm(scaled_int_Intention ~ RC + CCA + RC*CCA+ scaled_PB_w + scaled_Trust_w + scaled_SB_w + scaled_EC_w + scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  homeowners_con_data)

# Call the function and get the results
results_model2b <- multiple_regression_summary(model2b)
#results_model2b
```

```{r}
update_excel(wb2, "Message Interactions", results_model2a, results_model2b)
```

#### Third include interactions between messages and beliefs

```{r}
model3a <- lm(scaled_int_Interest ~  RC + CCA + RC*CCA + scaled_PB_w + RC*scaled_PB_w + scaled_SB_w + RC*scaled_SB_w + scaled_Trust_w + CCA*scaled_Trust_w + RC*scaled_Trust_w + scaled_EC_w  + scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  homeowners_con_data)

results_model3a <- multiple_regression_summary(model3a)
#results_model3a
```

```{r}
model3b <- lm(scaled_int_Intention  ~  RC + CCA + RC*CCA + scaled_PB_w + RC*scaled_PB_w + scaled_SB_w + RC*scaled_SB_w + scaled_Trust_w + CCA*scaled_Trust_w + RC*scaled_Trust_w + scaled_EC_w  + scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  homeowners_con_data)

results_model3b <- multiple_regression_summary(model3b)
#results_model3b
```

```{r}
update_excel(wb2, "all Interactions", results_model3a, results_model3b)
```


```{r}
#export excel sheet
saveWorkbook(wb2, "Study3_Results/Linear_Reg_homeowners.xlsx", overwrite = TRUE)
```

## Modeling by controlling for PV ownership

```{r}
#repeat anovas time time filtering for homeowners
pvowners_con_data <- con_data %>% filter(have_solar_bin == 0)
```


#### First include only message related variables and maon effects
```{r}
# Fit a logistic regression model for interest
model1a <- lm( int_Interest ~ RC + CCA+  scaled_PB_w +  scaled_Trust_w +  scaled_SB_w + scaled_EC_w+  scaled_CNS_w +  scaled_CIJM_w +  scaled_SN_w +  scaled_TB_w +  scaled_inc_int+ scaled_edu_int +  scaled_age + scaled_bill, data =  pvowners_con_data)

# Call the function and get the results
results_model1a <- multiple_regression_summary(model1a)
#results_model1a

```
```{r}
# Fit a logistic regression model for interest
model1b <- lm(scaled_int_Intention ~ RC + CCA + scaled_PB_w + scaled_Trust_w + scaled_SB_w + scaled_EC_w+ scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  pvowners_con_data)

# Call the function and get the results
results_model1b<- multiple_regression_summary(model1b)
#results_model1b
```
```{r}
#EXPORT to excel

wb3 <- createWorkbook()

```


```{r}
update_excel(wb3, "Main Effects", results_model1a, results_model1b)
```

#### Second include interactions between messages

```{r}
# Fit a logistic regression model for interest
model2a <- lm(scaled_int_Interest ~ RC + CCA + RC*CCA+ scaled_PB_w + scaled_Trust_w + scaled_SB_w + scaled_EC_w+ scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  pvowners_con_data)

# Call the function and get the results
results_model2a <- multiple_regression_summary(model2a)
#results_model2a
```

```{r}
# Fit a logistic regression model for interest
model2b <- lm(scaled_int_Intention ~ RC + CCA + RC*CCA+ scaled_PB_w + scaled_Trust_w + scaled_SB_w + scaled_EC_w + scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  pvowners_con_data)

# Call the function and get the results
results_model2b <- multiple_regression_summary(model2b)
#results_model2b
```

```{r}
update_excel(wb3, "Message Interactions", results_model2a, results_model2b)
```

#### Third include interactions between messages and beliefs

```{r}
model3a <- lm(scaled_int_Interest ~  RC + CCA + RC*CCA + scaled_PB_w + RC*scaled_PB_w + scaled_SB_w + RC*scaled_SB_w + scaled_Trust_w + CCA*scaled_Trust_w + RC*scaled_Trust_w + scaled_EC_w  + scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  pvowners_con_data)

results_model3a <- multiple_regression_summary(model3a)
#results_model3a
```

```{r}
model3b <- lm(scaled_int_Intention  ~  RC + CCA + RC*CCA + scaled_PB_w + RC*scaled_PB_w + scaled_SB_w + RC*scaled_SB_w + scaled_Trust_w + CCA*scaled_Trust_w + RC*scaled_Trust_w + scaled_EC_w  + scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  pvowners_con_data)

results_model3b <- multiple_regression_summary(model3b)
#results_model3b
```

```{r}
update_excel(wb3, "all Interactions", results_model3a, results_model3b)
```


```{r}
#export excel sheet
saveWorkbook(wb3, "Study3_Results/Linear_Reg_pvowners.xlsx", overwrite = TRUE)
```


## Modeling by controlling for attentiveness

```{r}
#repeat anovas time time filtering for homeowners
attentive_con_data <- con_data %>% filter(attentive == 1)
```


#### First include only message related variables and maon effects
```{r}
# Fit a logistic regression model for interest
model1a <- lm( int_Interest ~ RC + CCA+  scaled_PB_w +  scaled_Trust_w +  scaled_SB_w + scaled_EC_w+  scaled_CNS_w +  scaled_CIJM_w +  scaled_SN_w +  scaled_TB_w +  scaled_inc_int+ scaled_edu_int +  scaled_age + scaled_bill, data =  attentive_con_data)

# Call the function and get the results
results_model1a <- multiple_regression_summary(model1a)
#results_model1a

```
```{r}
# Fit a logistic regression model for interest
model1b <- lm(scaled_int_Intention ~ RC + CCA + scaled_PB_w + scaled_Trust_w + scaled_SB_w + scaled_EC_w+ scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  attentive_con_data)

# Call the function and get the results
results_model1b<- multiple_regression_summary(model1b)
#results_model1b
```
```{r}
#EXPORT to excel

wb4 <- createWorkbook()

```


```{r}
update_excel(wb4, "Main Effects", results_model1a, results_model1b)
```

#### Second include interactions between messages

```{r}
# Fit a logistic regression model for interest
model2a <- lm(scaled_int_Interest ~ RC + CCA + RC*CCA+ scaled_PB_w + scaled_Trust_w + scaled_SB_w + scaled_EC_w+ scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  attentive_con_data)

# Call the function and get the results
results_model2a <- multiple_regression_summary(model2a)
#results_model2a
```

```{r}
# Fit a logistic regression model for interest
model2b <- lm(scaled_int_Intention ~ RC + CCA + RC*CCA+ scaled_PB_w + scaled_Trust_w + scaled_SB_w + scaled_EC_w + scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  attentive_con_data)

# Call the function and get the results
results_model2b <- multiple_regression_summary(model2b)
#results_model2b
```

```{r}
update_excel(wb4, "Message Interactions", results_model2a, results_model2b)
```

#### Third include interactions between messages and beliefs

```{r}
model3a <- lm(scaled_int_Interest ~  RC + CCA + RC*CCA + scaled_PB_w + RC*scaled_PB_w + scaled_SB_w + RC*scaled_SB_w + scaled_Trust_w + CCA*scaled_Trust_w + RC*scaled_Trust_w + scaled_EC_w  + scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  attentive_con_data)

results_model3a <- multiple_regression_summary(model3a)
#results_model3a
```

```{r}
model3b <- lm(scaled_int_Intention  ~  RC + CCA + RC*CCA + scaled_PB_w + RC*scaled_PB_w + scaled_SB_w + RC*scaled_SB_w + scaled_Trust_w + CCA*scaled_Trust_w + RC*scaled_Trust_w + scaled_EC_w  + scaled_CNS_w + scaled_CIJM_w + scaled_SN_w + scaled_TB_w + scaled_inc_int+scaled_edu_int + scaled_age +scaled_bill, data =  attentive_con_data)

results_model3b <- multiple_regression_summary(model3b)
#results_model3b
```

```{r}
update_excel(wb4, "all Interactions", results_model3a, results_model3b)
```


```{r}
#export excel sheet
saveWorkbook(wb4, "Study3_Results/Linear_Reg_attentive.xlsx", overwrite = TRUE)
```

